Carrier phase and amplitude estimation of $M$-ary phase shift keying using pilots and data

### 2012-05-13 paper.tex
Added to paper. Also added mathemtica file for computing some specific formula when the noise is Gaussian.

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\lambda_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $m_L = \hat{\rho} - \rho_0 G(0)$. If the periodic function $g\fracpart{\phi}_{\pi}$ is continuous at multiples of $\tfrac{\pi}{M}$, then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = ?
\]
as $L \rightarrow \infty$.
\end{theorem}

@@

\begin{IEEEproof} (Theorem~\ref{thm:normality})
The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at half integers.  This precludes the use of ``standard approaches'' to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989}.  However, we show in Lemma~\ref{lem:diffatlambdaL} that the derivative does exist, and is equal to zero, at the maximiser $\hat{\lambda}_L$, so
\begin{align*}
G_L^\prime(\hat{\lambda}_L) &= 0 \\
&= \frac{1}{L} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\lambda + \Phi_i}.
\end{align*}
Define the function $Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0)$ and write
\begin{align*}
0 &= G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) + Q(\hat{\lambda}_L) \\
&= \sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) + \sqrt{L}Q(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( ?  + o_P(1) \big)
\]
where $o_P(1)$ denotes a number converging in probablity to zero as $L \rightarrow \infty$.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
It follows that
\[
0 = o_P(1) + \sqrt{L}G_L^\prime(0) + \sqrt{L} \hat{\lambda}_L \big( ?  + o_P(1) \big)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L = o_P(1) + \frac{\sqrt{L}G_L'(0)}{?  + o_P(1)}.
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance
\[
p \prob R_1^2 \sin^2(\Phi_1) + d \prob R_1^2 \sin^2\fracpart{\Phi_1}
\]
and it follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{p \prob R_1^2 \sin^2(\Phi_1) + d \prob R_1^2 \sin^2\fracpart{\Phi_1}}{?}
\]
as required.

@@

\begin{lemma}
\[
\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{1}{2M} - \frac{1}{2LM ?}
\]
for all $i \in D$.
\end{lemma}
\begin{proof}
Recall that $\hat{d}_i = \hat{d}_i(\hat{\theta})$ are the minimsers of $SS$.  The proof now proceeds by contradiction.  Assume that $\sfracpart{\hat{\lambda}_L + \Phi_i} \leq \frac{1}{2M} - \frac{1}{2LM ?}$ for some $k$.  Put $r_i = \hat{d}_i e_k$, then
\begin{align*}
Y(\{ r_i, i \in D\}) = \frac{1}{L}\left( B + \sum_{i \in D} y_i\hat{r}_i^* \right) = \hat{Y} + \frac{1}{L}\eta y_k\hat{d}_k^*.
\end{align*}
where we put $\hat{Y} = Y(\{ \hat{d}_i, i \in D\})$.  Now,
\begin{align*}
SS&(\{r_i, i \in D\}) \\
&= A - \frac{1}{L} \abs{ Y(\{ r_i, i \in D\}) }^2 \\
&= A - \frac{1}{L} \abs{ \hat{Y} + \frac{1}{L} \eta y_k\hat{d}_k^* }^2 \\
&= A - \frac{1}{L}\abs{\hat{Y}}^2 - \frac{2}{L^2}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) -  \frac{1}{L^3}\abs{ \eta y_k \hat{d}_k^* }^2\\
&= SS(\{\hat{d}_i, i \in D\}) - R
\end{align*}
where 
\[
R = \frac{2}{L^2}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) +  \frac{1}{L^3}\abs{ \eta y_k \hat{d}_k^* }^2.
\]
We will show that $R$ is positive, from which is will follow that $SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\})$, violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.

To see that $R$ is positive write
 \begin{align*}
R &\geq  \frac{2}{L^2}\abs{\hat{Y} y_k}\Re\left(\eta e^{j(\phi_i - \hat{\theta})}\hat{d}_k^* \right) +  \frac{1}{L^3}\abs{ \eta}^2 \abs{ y_k }^2 \\
 &= \frac{1}{L^2}\abs{y_k} \left( 2\abs{\hat{Y}}\Re\left(\eta e^{j(\phi_i - \hat{\theta})} \hat{d}_k^* \right) + \frac{1}{L}\abs{ \eta}^2 \abs{ y_k }  \right) 
 \end{align*}
 so it is sufficient to show that
 \[
 \Re\left(\eta e^{j(\phi_i - \hat{\theta})} \hat{d}_k^* \right) > - \frac{\abs{ \eta}^2 \abs{ y_k }}{2 L \abs{\hat{Y}}}.
 \]
 Unfinished, but this proof will work
\end{proof}

\begin{lemma}\label{lem:Qconv}
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( ph_1(0) + ?  + o_P(1) \big)
\]
\end{lemma}
\begin{IEEEproof}
Write
\[
Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0) = \frac{\abs{P}}{L} k_1(\lambda) + \frac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align*}
k_1(\lambda) &= \prob R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \\
k_2(\lambda) &= \prob R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big).
\end{align*}
Since
\[
\sin(\lambda + \phi) - \sin(\phi) = \lambda \big( \cos(\phi) + \zeta(\lambda) \big)
\]
where $\zeta(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero, then
\begin{align*}
k_1(\lambda) &= \prob R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \prob R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \prob R_1 \big) \\
&= \lambda \big( h_1(0) \; + \; \zeta(\lambda) K \big),
\end{align*}
where we put $K = \prob R_1$, a finite constant.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\begin{align*}
k_1(\hat{\lambda}_L) &= \hat{\lambda}_L \big( h_1(0) \; + \; \zeta(\hat{\lambda}_L) K \big) \\
&= \hat{\lambda}_L \big( h_1(0)  + o_P(1)\big).
\end{align*}
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocc} BLERG
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance
\[
p \prob R_1^2 \sin^2(\Phi_1) + d \prob R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} G_L^\prime(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
It follows from the standard central limit that the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) = \sqrt{\frac{\abs{P}}{L}} \frac{1}{\sqrt{\abs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $k_1(0) = 0$ and variance 
\[
p \prob R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin(\lambda + \Phi_i) = \sqrt{\frac{\abs{D}}{L}} \frac{1}{\sqrt{\abs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $k_2(0) = 0$ and variance
\[
d \prob R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

@@

\begin{lemma}\label{lem:XL} 
The distribution of $X_L$ converges to the normal with zero mean and covariance
\[
?
\]
as $L \rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

\begin{lemma}\label{lem:XLcovlambdaL} 
The covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ converges to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

>>>>

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\lambda_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $m_L = \hat{\rho} - \rho_0 G(0)$. If the periodic function $g\fracpart{\phi}_{\pi}$ is continuous at $\phi = (2k+1)\tfrac{\pi}{M}$ for every integer $k$, then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = \frac{1}{(p + H d)^2} \left( \begin{array}{cc} 
A_1 + A_2 & ? \\
? & ?
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\]
and
\[
A_1 = \prob R_1^2\sin^2(\Phi_1), \qquad A_2 = \prob R_1^2\sin^2\fracpart{\Phi_1}.
\]
\end{theorem}

@@

\begin{IEEEproof} (Theorem~\ref{thm:normality})
The proof is complicated by the fact that $G_L$ is not differentiable everywhere due to the function $\fracpart{\cdot}$ not being differentiable at half integers.  This precludes the use of ``standard approaches'' to proving normality that are based on the mean value theorem~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats,Pollard_new_ways_clts_1986,Pollard_conv_stat_proc_1984,Pollard_asymp_empi_proc_1989}.  However, we show in Lemma~\ref{lem:diffatlambdaL} that the derivative does exist, and is equal to zero, at the maximiser $\hat{\lambda}_L$, so
\begin{align*}
G_L^\prime(\hat{\lambda}_L) &= 0 \\
&= \frac{1}{L} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \sin\sfracpart{\lambda + \Phi_i}.
\end{align*}
Define the function $Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0)$ and write
\begin{align*}
0 &= G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) + Q(\hat{\lambda}_L) \\
&= \sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) + \sqrt{L}Q(\hat{\lambda}_L).
\end{align*}
Lemma~\ref{lem:Qconv} shows that
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $o_P(1)$ denotes a number converging in probablity to zero as $L \rightarrow \infty$.  Lemma~\ref{lem:empiricprocc} shows that
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
It follows that
\[
0 = o_P(1) + \sqrt{L}G_L^\prime(0) + \sqrt{L} \hat{\lambda}_L \big( p + Hd  + o_P(1) \big)
\]
and rearranging gives,
\[
\sqrt{L} \hat{\lambda}_L = o_P(1) + \frac{\sqrt{L}G_L'(0)}{p + Hd  + o_P(1)}.
\]
Lemma~\ref{lem:convdistGLdash} shows that the distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance
\[
p \prob R_1^2 \sin^2(\Phi_1) + d \prob R_1^2 \sin^2\fracpart{\Phi_1}
\]
and it follows that the distribution of $\sqrt{L}\hat{\lambda}_L$ converges to the normal with zero mean and variance
\[
\frac{p \prob R_1^2 \sin^2(\Phi_1) + d \prob R_1^2 \sin^2\fracpart{\Phi_1}}{?}
\]
as required.

@@

\begin{lemma}
\[
\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{1}{2M} - \frac{1}{2LM ?}
\]
for all $i \in D$.
\end{lemma}
\begin{IEEEproof}
Recall that $\hat{d}_i = \hat{d}_i(\hat{\theta})$ are the minimsers of $SS$.  The proof now proceeds by contradiction.  Assume that $\sfracpart{\hat{\lambda}_L + \Phi_i} \leq \frac{1}{2M} - \frac{1}{2LM ?}$ for some $k$.  Put $r_i = \hat{d}_i e_k$, then
\begin{align*}
Y(\{ r_i, i \in D\}) = \frac{1}{L}\left( B + \sum_{i \in D} y_i\hat{r}_i^* \right) = \hat{Y} + \frac{1}{L}\eta y_k\hat{d}_k^*.
\end{align*}
where we put $\hat{Y} = Y(\{ \hat{d}_i, i \in D\})$.  Now,
\begin{align*}
SS&(\{r_i, i \in D\}) \\
&= A - \frac{1}{L} \abs{ Y(\{ r_i, i \in D\}) }^2 \\
&= A - \frac{1}{L} \abs{ \hat{Y} + \frac{1}{L} \eta y_k\hat{d}_k^* }^2 \\
&= A - \frac{1}{L}\abs{\hat{Y}}^2 - \frac{2}{L^2}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) -  \frac{1}{L^3}\abs{ \eta y_k \hat{d}_k^* }^2\\
&= SS(\{\hat{d}_i, i \in D\}) - R
\end{align*}
where 
\[
R = \frac{2}{L^2}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) +  \frac{1}{L^3}\abs{ \eta y_k \hat{d}_k^* }^2.
\]
We will show that $R$ is positive, from which is will follow that $SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\})$, violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.

To see that $R$ is positive write
 \begin{align*}
R &\geq  \frac{2}{L^2}\abs{\hat{Y} y_k}\Re\left(\eta e^{j(\phi_i - \hat{\theta})}\hat{d}_k^* \right) +  \frac{1}{L^3}\abs{ \eta}^2 \abs{ y_k }^2 \\
 &= \frac{1}{L^2}\abs{y_k} \left( 2\abs{\hat{Y}}\Re\left(\eta e^{j(\phi_i - \hat{\theta})} \hat{d}_k^* \right) + \frac{1}{L}\abs{ \eta}^2 \abs{ y_k }  \right) 
 \end{align*}
 so it is sufficient to show that
 \[
 \Re\left(\eta e^{j(\phi_i - \hat{\theta})} \hat{d}_k^* \right) > - \frac{\abs{ \eta}^2 \abs{ y_k }}{2 L \abs{\hat{Y}}}.
 \]
 Unfinished, but this proof will work
\end{IEEEproof}

\begin{lemma}\label{lem:Qconv}
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where 
\[
H = 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\]
\end{lemma}
\begin{IEEEproof}
Write
\[
Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0) = \frac{\abs{P}}{L} k_1(\lambda) + \frac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align}
k_1(\lambda) &= \prob R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \nonumber\\
k_2(\lambda) &= \prob R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big). \label{eq:k2def}
\end{align}
Since,
\[
\sin(\lambda + \phi) - \sin(\phi) = \lambda \big( \cos(\phi) + \zeta(\lambda) \big),
\]
where $\zeta(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero, then
\begin{align*}
k_1(\lambda) &= \prob R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \prob R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \prob R_1 \big) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) K \big),
\end{align*}
since $h_1(0) = \prob R_1\cos(\Phi_1) = 1$ and where we put $K = \prob R_1$, a finite constant.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) K \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big).
\]
Lemma~\ref{lem:k2} shows that
\[
k_2(\hat{\lambda}_L) = \hat{\lambda}_L \big( ? \; + \; o_P(1) \big).
\]
\end{IEEEproof}

\begin{lemma}\label{lem:k2}
With the function $k_2(\lambda)$ defined as in~\eqref{eq:k2def}, then
\[
k_2(\hat{\lambda}_L) = \hat{\lambda}_L \big( H \; + \; o_P(1) \big).
\]
where
\[
H = 2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\]
\end{lemma}
\begin{IEEEproof}
Now, if $0 \leq \lambda < \tfrac{\pi}{M}$, then for each integer $k$,
\begin{align*}
\sin\fracpart{\lambda + \phi} - \sin\fracpart{\phi} &= \sin(\lambda + \phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi k}{M}) \\
&= \lambda\big(\cos(\phi - \tfrac{2\pi k}{M}) + \zeta_k(\lambda)\big) \\
&= \lambda\big(\cos\fracpart{\phi} + \zeta_k(\lambda)\big)
\end{align*}
when $\phi \in [\tfrac{ (2k-1)\pi}{M}, \tfrac{(2k+1)\pi}{M} - \lambda )$ and 
\begin{align*}
\sin&\fracpart{\lambda + \phi} - \sin\fracpart{\phi} \\
&= \sin(\lambda + \phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi (k-1)}{M}) \\
&=  v_k(\phi) + \lambda\big(\cos(\phi - \tfrac{2\pi k}{M}) + \zeta_k(\lambda)\big) \\
&= v_k(\phi) + \lambda\big(\cos\fracpart{\phi} + \zeta_k(\lambda)\big)
\end{align*}
when $\phi \in [ \tfrac{(2k+1)\pi}{M} - \lambda,\tfrac{(2k+1)\pi}{M} )$, and where
\[
v_k(\phi) = \sin(\phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi (k-1)}{M}).
\]
Observe that $v_k(\tfrac{(2k+1)\pi}{M}) = 2\sin(\tfrac{\pi}{M})$.  We can now write
\[
\sin\fracpart{\lambda + \phi} - \sin\fracpart{\phi} = v(\lambda, \phi) + \lambda\cos\fracpart{\phi}
\]
where $v(\lambda, \phi) = \sum_{k\in\ints} v_k(\lambda, \phi)$ and where
\[
v_k(\lambda,\phi) = \begin{cases}
v_k(\phi) + \lambda\zeta_k(\lambda) &  \phi \in [ \tfrac{(2k+1)\pi}{M} - \lambda,\tfrac{(2k+1)\pi}{M} ) \\
\lambda\zeta_k(\lambda) & \phi \in [\tfrac{ (2k-1)\pi}{M}, \tfrac{(2k+1)\pi}{M} - \lambda ) \\
0 & \text{otherwise}.
\end{cases}
\]
Now
\begin{align*}
k_2(\lambda) &=  \prob R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big) \\
&= \prob R_1\big( v(\lambda, \Phi_1) + \lambda\cos\fracpart{\Phi_1} \big) \\
&= \prob R_1 v(\lambda, \Phi_1) + \lambda h_2(0).
\end{align*}
It remains to evaluate $\prob R_1 v(\lambda, \Phi_1)$.  Recalling that $f(r,\phi)$ is the joint probability density function of $R_1$ and $\Phi_1$,
\begin{align*}
k_2(\lambda) &= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \\
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi.
\end{align*}
Since $v(\lambda, \phi) = \sum_{k\in\ints} v_k(\lambda, \phi)$,
\[
k_2(\lambda) = \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi
\]
and since $v_k(\lambda,\phi) = 0$ for $\phi \in [0,2\pi)$ when $k \notin \{0,1,\dots,M\}$ the infinite sum above can be truncated so that
\[
k_2(\lambda) = \sum_{k = 0}^M \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi
\]
Now
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = &\int_{\tfrac{(2k+1)\pi}{M} - \lambda}^{\tfrac{(2k+1)\pi}{M}}v_k(\phi)g(\phi)d\phi \\
&\hspace{0.5cm}+ \lambda\zeta_k(\lambda) \int_{\tfrac{(2k-1)\pi}{M}}^{\tfrac{(2k+1)\pi}{M}}g(\phi)d\phi.
\end{align*}
Now, since $g\fracpart{\phi}_\pi$ is continuous at $(2k+1)\tfrac{\pi}{M}$ for each integer $k$, and $v_k(\phi)$ is continuous and $v_k(\tfrac{(2k+1)\pi}{M}) =  2\sin(\tfrac{\pi}{M})$,
\begin{align*}
\int_{\tfrac{(2k+1)\pi}{M} - \lambda}^{\tfrac{(2k+1)\pi}{M}}v_k(\phi)g(\phi)d\phi &= \lambda( v_k(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) ) \\
&= \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) )
\end{align*}
where $\nu_k(\lambda)$ is function that goes to zero as $\lambda$ goes to zero.  To keep the notation clean put $A_k = \int_{\tfrac{(2k-1)\pi}{M}}^{\tfrac{(2k+1)\pi}{M}}g(\phi)d\phi$.  For each $k\in\ints$, $A_k$ is a nonnegative finite constant less than one.  Now
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi \\
&= \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) + \zeta_k(\lambda) A_k )
\end{align*}
and
\begin{align*}
k_2(\lambda) &= \sum_{k = 0}^M \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) + \zeta_k(\lambda) A_k ) \\
 &= \epsilon(\lambda) + 2 \lambda \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\end{align*}
where $\epsilon(\lambda) = \sum_{k=0}^M\big( \nu_k(\lambda) + \zeta_k(\lambda) A_k \big)$ is a function that goes to zero as $\lambda$ goes to zero.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\epsilon(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\epsilon(\hat{\lambda}_L) = o_P(1)$.  So
\[
k_2(\hat{\lambda}_L) = o_P(1) + 2 \hat{\lambda}_L \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\]
as required.
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocc} BLERG
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}G_L'(0)$ converges to the normal with zero mean and variance $A_1 + A_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} G_L^\prime(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
It follows from the standard central limit that the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\lambda + \Phi_i) = \sqrt{\frac{\abs{P}}{L}} \frac{1}{\sqrt{\abs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $k_1(0) = 0$ and variance 
\[
p \prob R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin(\lambda + \Phi_i) = \sqrt{\frac{\abs{D}}{L}} \frac{1}{\sqrt{\abs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $k_2(0) = 0$ and variance
\[
d \prob R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

@@

\begin{lemma}\label{lem:XL} 
The distribution of $X_L$ converges to the normal with zero mean and covariance
\[
?
\]
as $L \rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}

\begin{lemma}\label{lem:XLcovlambdaL} 
The covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ converges to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}

\section{The Gaussian noise case}

Let the noise sequence $\{w_i\}$ be complex Gaussian with independent real and imaginary parts having zero mean and variance $\sigma^2$.  The joint density function of the real and imaginary parts is then
\[
p(x,y) = \frac{1}{2\pi\sigma^2}e^{-(x^2 + y^2)/\sigma^2}
\]
Theorem~\ref{thm:consistency}~and~\ref{thm:normality} hold and, since the distribution of $w_1$ is circularly symetric, the distribution of $R_1e^{j\Phi_1}$ is identical to the distribution of $1 + \frac{1}{\rho_0} w_1$.
%and the joint density function of the real and imaginary parts of $Z$ is
%\[
%p_Z(x,y) = \rho_0^2 p( \rho_0 (x - 1), \rho_0 y ) = \frac{\kappa^2}{2\pi}e^{-\kappa^2(x ^2 - 2x + 1 + y^2) }
%\] 
%where $\kappa = \tfrac{\rho_0}{\sigma}$.  
It can be shown that
\[
g(\phi) = \frac{\cos^2(\phi)}{4\sqrt{\pi}}\left( \frac{e^{-\kappa^2} }{\sqrt{\pi}} + \kappa \Psi(\phi)  e^{-\kappa^2\sin^2(\phi)}\cos(\phi) \right)
\]
where
\[
\Psi(\phi) = 1 + \erf(\kappa \cos(\phi)) = 1 + \frac{2}{\sqrt{\pi}}\int_0^{\kappa \cos(\phi)} e^{-t^2} dt .
\]
The value of $A_1$ and $A_2$ can be computed by numerical integration.
